### 2021-01-25 papers/jin-thesis/Chapters/2Theory.tex
Progress on thesis and reverted changes for generate paper model figures

\subsection{Domains as Angular Springs}
In order to best simulate the stretching and forward kicking motion of the power stroke, we define our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain. This can be analogous to how humans walk as the domains are used as flexible joints when taking a step. Defining our domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law: 
\begin{equation}
    F_i=-c_i(\theta_i-\theta_{i,eq})
\end{equation}
where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion. Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
\begin{equation} \label{eq:energy}
    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
\end{equation}
%Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e. $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains. 
This equation would then be used throughout the entirety of the simulation to determine the total energy of our dynein at a given conformation.

@@

The key difference between the works discussed in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state. Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk. However, they noticed that their simulation took significant computation time because of the unbinding process taking a large amount of time relative to the total stepping time. They also noticed that the both bound configuration of dynein does not impact the final step length. We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.

@@

The secondary force that we can easily identify is the random force inspiring the Brownian motion. This force describes the random interactions the domains experience with the paticles making the solvent and will be denoted as \textbf{F}$_{rand}$. The ``randomness" will be sampled from a zero-centered Gaussian with variance:
\begin{equation}
	\sigma^2=\sqrt{\frac{2\gamma}{\beta\Delta t}}.
\end{equation}
where $\beta$ is the thermodynamic beta and $\Delta t$ is a time-step.

@@

\subsection{Monte Carlo Algorithm}
Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding. This allows us to use Monte Carlo methods for analyzing a single step by interpreting our model as a system. Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates. For this model, the dynein is the system and the different possible microstates are the both bound configurations our model can achieve. Each both bound configuration are independent from one another and can produce different total energy values. The benefit of this method is the ability to sample a large ensemble of both bound states and quickly generate statitics about the step. Eventually, this will allow us to create probability distributions for important variables. The algorithm is as follows:
\begin{algorithm}[H]
	\caption{Monte Carlo}
	\label{alg:MonteCarlo}

	\begin{alg}
	\item Initialize an unsigned distance, L, between the binding domains.

	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})

	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.

	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate both bound state angles with the naming convention in Figure (\ref{fig:OBvsBB}).

	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eq:energy})).
	\begin{equation}
		E_{total, n}=\sum_{i}\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
	\end{equation}
	Here, $n$ refers to the specific both bound configuration.

	\item Define a Boltzmann distribution for the relative probability of unbinding and a partition function, $Z$.
	\begin{equation}
		P_{ub}\propto e^{-\beta E_{total, n}}
	\end{equation}
	\begin{equation}
		Z=\sum_{n}e^{\beta E_{total, n}}
	\end{equation}

	\item Calculate the probability of unbinding with the unbinding rate and Boltzmann distribution.
	\begin{equation}
		P_{ub} = \rho_{ub}e^{-\beta E_{total, n}}
	\end{equation}

	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 1.

	\item If dynein unbinds, run one bound Brownian dynamics simulation of the step and wait until rebinding.

	\item Collect statistics about final displacement and one bound time.

	\end{alg}

\end{algorithm}

>>>>

\subsection{Domains as Angular Springs}
In order to best simulate the stretching and forward kicking motion of the power stroke, we define our domains to act as springs with spring constants $c_b$, $c_m$, and $c_t$ -- one for each respective domain. This can be analogous to how humans walk as the domains are used as flexible joints when taking a step. Defining our domains as springs will also allow us to influence forward bias walking by introducing a restoring force in each domain using Hooke's law: 
\begin{equation}
    F_i=-c_i(\theta_i-\theta_{i,eq})
\end{equation}
where $c_i$ is the spring constant, $\theta_i$ is angle corresponding to the $i^{th}$ domain, and $\theta_{i,eq}$ is the equilibrium angle in which biases the motion. Using this, we can calculate the energy of each domain by integrating and arriving to the familiar equation for spring energy.
\begin{equation} \label{eqn:energy}
    U_i=\frac{1}{2}c_i(\theta_i-\theta_{i,eq})^2
\end{equation}
%Since dynein is symmetric for each heavy chain leg, the equilibrium angle will be identical for both binding and motor domain pairs, i.e. $\theta_{b,eq}$ is defined as the equilibrium angle for both binding domains, while $\theta_{m,eq}$ is defined as the equilibrium angle for both motor domains. 
This equation would then be used throughout the entirety of the simulation to determine the total energy of our dynein at a given conformation.

@@

The key difference between the works discussed in \cite{Capek2017, } (\textit{Elliott and John's paper}) and this paper is the implementation of a Monte Carlo algorithm in replacement for the Brownian dynamics both bound state. Capek and Waczak were able to fully simulate both states of dynein's walk with a Brownian dynamics simulation and collect data of multiple steps during a walk. However, they noticed that the unbinding process took a large amount of computation time relative to the total stepping time. They also noticed that the both bound configuration of dynein does not impact the final step length. We developed this new method of analyzing the both bound state to significantly improve computational efficiency while still maintaining the dynamical simulation of the actual step in the one bound state.

@@

The secondary force that we can easily identify is the random force inspiring the Brownian motion. This force describes the random interactions the domains experience with the paticles making the solvent. It will be denoted as \textbf{F}$_{rand}$, and the ``randomness" will be sampled from a zero-centered Gaussian with variance:
\begin{equation}
	\sigma^2=\sqrt{\frac{2\gamma}{\beta\Delta t}}.
\end{equation}
where $\beta$ is the thermodynamic beta and $\Delta t$ is a time-step.

@@

\subsection{Monte Carlo for Both Bound}
Since research and Waczak/Capek suggests that the dynein spends the majority of the stepping time in the both bound state, we can safely assume that the dynein equilibriates before unbinding. This inspired us to use Monte Carlo methods for analyzing dynein's step by interpreting our model as a system. Typically, Monte Carlo methods are used to analyze equilibrium theromodynamics of fluids where a system of atoms can possess many different microstates. For this model, the dynein is the system and the different possible microstates are the many both bound configurations our model can achieve. However, unlike the more commonly known Markov Chain Monte Carlo, each both bound configuration are independent from one another and can produce different total energy values. The benefit of this method is the ability to sample a large ensemble of both bound configurations and quickly generate stepping statitics. Eventually, this will allow us to create probability distributions for important variables.

With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression. That is, 
\begin{equation}
	P_{ub}\propto e^{-\beta E_{total}}.
\end{equation}
With this Boltzmann factor, we can also generate a partition function, 
\begin{equation} \label{eqn:partition}
	Z=\sum_{i}e^{-\beta E_{total,i}},
\end{equation}
where $i$ refers to the specific both bound configuration. In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well. The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics. With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time. The equations to do so are all shown below in that order:
\begin{equation}
	\langle\rho_{ub, n}\rangle=\frac{\sum_{i}\rho_{ub, n} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, f}\rangle=\frac{\sum_{i}\rho_{ub, f} e^{-\beta E_{total,i}}}{Z}
\end{equation}
\begin{equation}
	\langle P_{ub, n}(L)\rangle = \frac{\langle\rho_{ub, n}\rangle}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}
\end{equation}
\begin{equation}
	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}.
\end{equation}

### 2021-01-25 papers/jin-thesis/Chapters/3Methods.tex
Progress on thesis and reverted changes for generate paper model figures

\textit{All code for simulation can be accessed from GitHub through this link:}

\section{Simulation}
\textit{Picking Random angles to create random distribution of dynein configurations. Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound. It is done this way in order for MC to generate ensemble of data rather quickly.}\\
\textit{Include a flow chart.}

\section{Time Evolution}
\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}

@@

@@

>>>>

%\textit{All code for simulation can be accessed from GitHub through this link:}

The entire model and simulation code can be found here on \url{https://github.com/kiatvonj/dynein_walk}, where the model and simulation were coded using both Python and C++. The both bound Monte Carlo was coded on Python due to the calculations being less computationally rigorous and time independent, while the one bound Brownian dynamics was coded on C++ to utilize the faster computation speed for the time  dependent Brownian motion.

\section{Simulation}
%\textit{Picking Random angles to create random distribution of dynein configurations. Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound. It is done this way in order for MC to generate ensemble of data rather quickly.}\\
%\textit{Include a flow chart.}
Since we want to generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk. This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step. The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculate the total energy. If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics. Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step. However, the big caveat with this method is that we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations. This will force the measured probabilities to be a function of $L$ and will be addressed later in Section (\ref{sec:DataAna}). The algorithm for the both bound process is shown below:

\begin{algorithm}[H]
	\caption{Monte Carlo Both Bound}
	\label{alg:MonteCarlo}

	\begin{alg}
	\item Initialize an unsigned distance, $L$, between the binding domains.

	\item Randomly pick 4 angles ($\theta_0$, $\theta_1$, $\theta_2$, $\theta_3$) to generate a completely random configuration of dynein in space. (\textit{Include picture})

	\item Calculate the distance between the binding domains and check if the distance is within a range of $L\pm l$, where $l$ is arbitrarily small.

	\item Rotate the configuration so that both binding domains are on the microtubule and recalculate angles with the naming convention in Figure (\ref{fig:OBvsBB}).

	\item Calculate the total energy of the configuration by summing the energy of each domain (using Equation (\ref{eqn:energy})),
	\begin{equation}
		E_{total, i}=\sum_{k}\frac{1}{2}c_k(\theta_k-\theta_{k,eq})^2.
	\end{equation}
	Here, $i$ refers to the specific both bound configuration and $k$ is the domain.

	\item Calculate the relative unbinding probability from a Boltzmann distribution and add a term to the partition function:
	\begin{equation}
		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, n}}\kappa,
	\end{equation}
	\begin{equation}
		Z=\sum_{n}e^{\beta E_{total, n}}.
	\end{equation}
	We defined a $\kappa$ to normalize the relative unbinding probability and keep it less than 1.

	\item ``Roll a die" for a value within the range of $[0,1]$ and check if the value is less than $P_{ub}$. If not, repeat algorithm from step 2.

	\item If dynein unbinds, initialize the one bound state with the both bound configuration, run the Brownian dynamics simulation of the step, and wait until it rebinds.

	\item Collect statistics about final displacement and one bound time. Repeat algorithm from step 2.

	\end{alg}

\end{algorithm}

A more in-depth explanation and rigorous flow chart for the one bound Brownian dynamics simulation can be found here \cite{Capek2017, }.

%\section{Time Evolution}
%\textit{Simulate over a delta t during one bound and every iteration check for rebinding. How are the probabilities of binding and unbinding affected by the time.}

@@

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.3\columnwidth]{../../plots/burgess-model-figure.pdf}
	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} Left: the both bound model is superimposed over dynein micrograph. The arrow indicates 15nm. Image taken from \cite{burgess2003dynein}.  Right: cryo-electron tomograph of dynein with the one-bound model overlaid. Image taken from \cite{grotjahn}.} 
	\label{fig:ModelParams}
\end{figure}

@@

\section{Data Analysis} \label{sec:DataAna}
\begin{equation}
	p(x_i,x_f)=p(x_f|x_i)p(x_i)
\end{equation}
Bayes' Theorem
\begin{equation}
	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}
\end{equation}
\[
	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
\]\[
	p(x_i)=p(x_i|L_i)p(L_i)
\]
Detailed Balance Equation:
\begin{equation}
	p^n(L_i)=T^n(L_f|L_i)p^0(L_i)
\end{equation}
\begin{align}
	T(L_f|L_i)&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
	&=p(L_f|x_i)p(x_i|L_i)\\
	&=p(L_f|L_i)
\end{align}
